A comparison of simple models for urban morphogenesis

### 2020-12-06 Docs/Papers/MesoBenchmark/paper/paper.tex
rerun
myoml_results
time_pse_expmixture

@@

The models are implemented in \texttt{scala} and integrated into the \texttt{spatialdata} library for spatial sensitivity analysis \cite{raimbault2020scala}. The library is bundled as an OpenMOLE plugin for the numerical experiments. OpenMOLE is an open source software for model exploration and validation \cite{reuillon2013openmole} combining model embedding with state-of-the-art exploration methods (including for example sensitivity analysis, design of experiments, calibration with genetic algorithms) and a transparent distribution of computations on high performance computing environments. In our case, we use its workflow system and an integrated algorithm to determine the feasible space of models. Source code for models is available in the open source code of the \texttt{spatialdata} library at \url{https://github.com/openmole/spatialdata}. Source code for numerical experiments, simulation data and results used in this paper are available on an open git repository at \url{https://github.com/JusteRaimbault/UrbanGrowth}.

@@

We now turn to the main experiment of this paper: using a diversity search algorithm to determine the full feasible morphological space for each model. Therefore, we use the Pattern Space Exploration (PSE) algorithm \cite{cherel2015beyond} embedded in OpenMOLE. Diversity search was introduced in the field of artificial life as genetic algorithms with the aim to maximize diversity of the population \cite{lehman2008exploiting}. In the case of the PSE algorithm, a novelty criteria leads the search towards new regions of the indicator space, and results are stored in a hitmap. When running long enough, convergence in terms of number of solutions found is generally reached, and one can consider the final population as the feasible space of the model. We run here the algorithm up to 100,000 generations for each model, with grid of step 0.05 in the indicator space. Convergence was reached separately for each model.

@@

@@

>>>>

\cite{jun2020modling} entropy and urban growth

@@

The models are implemented in \texttt{scala} and integrated into the \texttt{spatialdata} library for spatial sensitivity analysis \cite{raimbault2020scala}. The library is bundled as an OpenMOLE plugin for the numerical experiments. OpenMOLE is an open source software for model exploration and validation \cite{reuillon2013openmole} combining model embedding with state-of-the-art exploration methods (including for example sensitivity analysis, design of experiments, calibration with genetic algorithms) and a transparent distribution of computations on high performance computing environments. In our case, we use its workflow system and an integrated algorithm to determine the feasible space of models. Source code for models is available in the open source code of the \texttt{spatialdata} library at \url{https://github.com/openmole/spatialdata}. Source code for numerical experiments, simulation data and results used in this paper are available on an open git repository at \url{https://github.com/JusteRaimbault/UrbanGrowth}. Full simulation data is available on the dataverse repository at \url{https://doi.org/10.7910/DVN/VVIEYO}.

@@

We now turn to the main experiment of this paper: using a diversity search algorithm to determine the full feasible morphological space for each model. Therefore, we use the Pattern Space Exploration (PSE) algorithm \cite{cherel2015beyond} embedded in OpenMOLE. Diversity search was introduced in the field of artificial life as genetic algorithms with the aim to maximize diversity of the population \cite{lehman2008exploiting}. In the case of the PSE algorithm, a novelty criteria leads the search towards new regions of the indicator space, and results are stored in a hitmap. When running long enough, convergence in terms of number of solutions found is generally reached, and one can consider the final population as the feasible space of the model. We run here the algorithm up to 100,000 generations for each model, with grid of step 0.05 in the indicator space. Convergence was reached separately for each model.
% equivalent in terms of Islands generation?
% which spatialdata commit? 4ef6bc7c4e7887bb35138773ae87b158e6e9a19b
% (replace plugin on myoml-27/08 16h52 + remove urbgrowth acc)
% latest 36fb676ce20f1ca6586defb9f8a15ea2a366477b
% (remove urbanevolution_2.12 29/04 15:03: pb compat) (remove saltelli exec - time ok)(remove zombiesbundle 31/08 9:55)

@@

Correlations/PCA for each model and for all points? (plus analysis in link to params? not possible in stoch? (does replication strain params? Y!)

@@

geodesign: uncertainty - compromises - no prediction models

\cite{10.1371/journal.pone.0242479} emissions - density: policies when linked to models?

\cite{d2019new}
